Government websites as data: A methodological pipeline for collection, processing, and text analysis

### 2017-12-28 paper/presentation/Markus_SPSA_2018_Presentation.tex
presentation

@@

\begin{frame}{Fightin' Words}
	\input{fightinwordsIN.tex} %../tables/stmTopWordsINDem.tex
\end{frame}

@@

\begin{frame}{Structural Topic Model}
\input{stmTopWordsINDem.tex} %../tables/stmTopWordsINDem.tex
\end{frame}

\begin{frame}{Structural Topic Model}
\input{stmTopWordsINRep.tex} %../tables/stmTopWordsINRep.tex
\end{frame}

>>>>

\begin{frame}{Data Overview}
\input{descriptiveStatsIN.tex}
\input{descriptiveStatsLA.tex}
\end{frame}

@@

\begin{frame}{Fightin' Words - Monroe et al. (2008)}
\linespread{1.5}
\begin{itemize}
	\item Goal: Split words based on one binary variable (party)
	\item Find the most Democratic and most Republican words
	\item Problem: Text mostly consists of meaningless words
	\item Solution: Set prior based on expected distribution of words in random text
	\item Method provides a z-Score indicating the degree to which a word is preferred by one party
	\item Very fast to compute
\end{itemize}
\end{frame}

\begin{frame}{Fightin' Words (Indiana)}
	\input{fightinwordsIN.tex}
%	\input{../tables/fightinwordsIN.tex}
\end{frame}

@@

\begin{frame}{Structural Topic Model - Roberts et al. (2014)}
\linespread{1.5}
\begin{itemize}
	\item Topic models find clusters of semantically related words in texts --> i.e. topics
	\item As a clustering method, LDA doesn't explicitly allow for covariates (although post-hoc comparison is possible)
	\item The structural topic model extends this approach to explicitly include (multiple) covariates
	\item Our covariates: Party + City Population
\end{itemize}
\end{frame}

\begin{frame}{Structural Topic Model (Indiana)}
\input{stmTopWordsINDem.tex} %../tables/stmTopWordsINDem.tex
\end{frame}

\begin{frame}{Structural Topic Model (Indiana)}
\input{stmTopWordsINRep.tex} %../tables/stmTopWordsINRep.tex
\end{frame}
